---
title: "Lab 03 Notebook"
author: "Christopher Prener, Ph.D."
date: '(`r format(Sys.time(), "%B %d, %Y")`)'
output: 
  github_document: default
  html_notebook: default 
---

## Introduction
This is the replication notebook for Lab-03 from the course SOC 4650/5650: Introduction to GISc. This file *does not* include the project set-up chunk. Instead, it uses `here` when data are loaded and/or saved.

## Load Dependencies
The following code loads the package dependencies for our analysis:

```{r package-load}
# tidyverse
library(ggplot2) # data plotting

# other packages
library(here) # working directory tools
library(sf) # spatial data tools
```

## Load Data
The following code loads the data package and assigns our data to a data frame in our global environment:

```{r data-load}
moBoundary <- st_read(here("data","MO_BOUNDARY_State.shp"), stringsAsFactors = FALSE)
```

## Part 1
### Question 8
The following code creates a basic plot of Missouri:

```{r missouri-plot}
ggplot() +
  geom_sf(data = moBoundary, fill = "#5d5d5d", color = "#5d5d5d")
```

This code block saves the map to the `results` subfolder:

```{r save-missouri-plot}
ggsave(here("results","missouriMap.png"), dpi = 300)
```

We now have a very simple map of Missouri saved in our project.